---
author: Arvind Venkatadri
date: '`r format(Sys.Date())`'
title: TRIZ Contradictions
subtitle: ': A Graphical Analysis'
output:
  html_document:
    toc_float: true
    number_sections: true
    theme: flatly
    toc: true
    code_download: true
    highlight: tango
keywords: TRIZ; Contradictions; R; tidygraph
abstract: A graphical analysis of the TRIZ Contradiction Matrix and the Inventive
  Principles
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(tidygraph)
library(ggraph)
```
# Introduction


# The 39 Parameters and 40 Inventive Principles

```{r}
params <- 
  readxl::read_xls("./TRIZ_Matrix.xls",sheet = "Matrix", range = "B3:B41",col_names = "param") %>% 
  rowid_to_column(var = "paramNo")
params

ips <- 
  readxl::read_xls("./TRIZ_Matrix.xls",sheet = "Matrix", range = "AR4:AS43", c("ipNo", "ip")) %>% 
  separate(., col = "ip", into = c("ip", NA),sep = ",", remove = TRUE) %>% mutate(ipNo = as.integer(ipNo))
ips

```


# Reading and Data Wrangling in the Contradiction Matrix
```{r}
matrix <-
  read_xls("./TRIZ_Matrix.xls", sheet = "Matrix", range = "C2:AO41") %>%
  rowid_to_column(var = "improve") %>%
  pivot_longer(.,
               cols = -improve,
               names_to = "not_worsen",
               values_to = "principles") %>% drop_na() %>%
  separate(
    .,
    col = principles,
    into = c("ip1", "ip2", "ip3", "ip4"),
    sep = ","
  ) %>% mutate(
    not_worsen = as.integer(not_worsen),
    ip1 = as.integer(ip1),
    ip2 = as.integer(ip2),
    ip3 = as.integer(ip3),
    ip4 = as.integer(ip4)
  )
matrix
```
We have the Contradiction Matrix in table form. The first two *columns* are the two Parameters, one which we want to Improve and  the other which we want to Not Worsen. For each of these combinations, the columns to the right give 3-4 Inventive Principles that could apply in this situation.


# Keeping the lower triangular part.
# C-matrix is (almost) symmetric about the main diagonal
matrix <- matrix %>% arrange(improve, not_worsen)




# Make the matrix long for plotting
matrix_long <- matrix %>% 
  pivot_longer(cols = ip1:ip4, 
               names_to = "names", 
               values_to = "ip") %>%
  select(-names) %>% 
  drop_na(ip) %>% left_join(., ips, by = c("ip" = "ipNo")) %>% 
  rename(ipName = ip.y)
matrix_long

```
There are many ways in which we can plot this matrix. 

1. All Parameters and all Inventive Principles.

2. Take each of the Parameters and see which of the Inventive Principles they are mostly connected to

3. Take each of the Inventive Principles and see which of the Parameters they are connected to.

4. Take the Top 10 most commonly used Inventive Principles and see how many of the Contradictions end with them

4. May be other visualizations...based non-engineering domains for example?

A. All Parameters and all Inventive Principles
```{r}

matrix_long %>% 
  rename(from = improve, to = not_worsen) %>% 
  tbl_graph(nodes = params, edges = .) %>% 
  ggraph( layout = "nicely") + 
  geom_edge_link0(alpha = 0.05) + 
  geom_node_point() + 
  geom_node_text(aes(label = paramNo), size = 6, color = "red", repel = TRUE)
```






B. Parameters to IP mapping

```{r}
matrix_long %>% 
  filter(ip == 10) %>% 
  tbl_graph(nodes = params, edges = .) %>% 
  ggraph( layout = "nicely") + geom_edge_fan0(alpha = 0.15) + geom_node_point() + geom_node_text(aes(label = paramNo), size = 3, colour = "red",repel = TRUE)
```

C. IP to Parameter mapping

```{r}
matrix_long %>% 
  filter(improve == "1" | not_worsen == "1") %>% 
  tbl_graph(nodes = params, edges = .) %>% 
  ggraph( layout = "nicely") + geom_edge_fan0(alpha = 0.15) + geom_node_point() + geom_node_text(aes(label = paramNo), size = 3, colour = "red",repel = TRUE)
```
